# Getting started with MRS

## Selected books for MRS, MRI& NMR

- R.A. de Graaf `In Vivo NMR Spectroscopy: Principles and Techniques`,John Wiley & Sons Ltd.,ThirdEdition, 2018(comprehensive and comprehendible overview of in vivo MR spectroscopy techniques; very extensive treatment of radiofrequency (RF) pulses including adiabatic RF pulses; probably thereference as a textbookfor MRS)
- P.B. Barker, A. Bizzi, N. De Stefano, R.Gullapalli, and D.D.M. Lin `Clinical MR Spectroscopy:Techniques and Applications`,Cambridge University Press,2010(describes underlying physical principles of MRS and provides a perceptive review of clinical MRS applications)
- R.W. Brown, Y.-C.N. Cheng, E.M. Haacke, M.R. Thompson, and R.Venkatesan `Magnetic Resonance Imaging: Physical Principles and Sequence Design`, New York: J. Wiley & Sons, c1999; 2ndEdition,2014 (excellent text that balances mathematical strictness and physics concepts with intuitional and technical explanations!!!;specific topics, such as fast spin echo, are treated toa lesser extent than desirable; only a few pages about MR spectroscopy)
- D.W. McRobbie, E.A. Moore, M.J. Graves and M.R. Prince`MRI From Proton to Picture`,Cambridge University Press, 2ndEdition, 2006 (comprehensive introduction to the basics of MR practice and theory; very comprehendible and with superb illustrations; one chapter about MR spectroscopy)
- P. Mansfield and P.G. Morris `NMR Imaging in Biomedicine`,New York: Academic Press, 1982(classic textbook with elegant treatment of NMR techniques, though too involved for a beginner)
- A. Abragam `The Principles of Nuclear Magnetism`, Oxford, 1961(standard text for quantum mechanical treatment of nuclear magnetism; requires good knowledge of quantum mechanics)Selected papers for MRS & NMR(to be completed):
- One of the first papers about the basic concepts of NMR:[1]
- The fundamental concept of an echo is introduced in:[2][1]F. Bloch, “Nuclear induction,” Physical Review, vol. 70, pp. 460-74, 1946.[2]E. L. Hahn, “Spin Echoes,” Physical Review, vol. 80, pp. 580, 1950

## Web links

**Here are some web links that lead to tutorials or introductory material for MR S& NMR:**

- https://www.cis.rit.edu/htbooks/nmr/

  (online book “The Basics of NMR” by Hornak with nice animations, intended for beginners)

- https://www.cis.rit.edu/htbooks/mri/

  (online book “The Basics of MRI” by Hornak with nice animations, intended for beginners)

- https://mrshub.org/

  (MRS hub of the ISMRM MR Spectroscopy Study Group)

- http://www.users.on.net/~spinupdownunder/spectroscopy/MRS.htm 

  (Adelaide web site for MR spectroscopy)

- https://www.imaios.com/en/e-Courses/e-MRI/Magnetic-Resonance-Spectroscopy-MRS 

  (very short e-MRI courseaboutMR spectroscopy, just as a start)

- http://www.simplyphysics.com/MARS/data/level_1/spectros.htm 

  (General MR Spectroscopy Acronym Directory)

## Educational Materials List

### MRS Workshop

- [Introduction to MRS]() by `Ulrike Dydak`

- [Basics of MRS]() by `Ariane Filmer`
- [Localization Methods]() by `Riemann`
- [Calib & Workflow]() by `Ariane Filmer`
- [Postprocessing & Quantification]() by `Georg Oeltzschner`
- [NeuroMet Mrs workshop literature list]()
- [High Field Workshop]() by `Heidelberg Kan`
- [MRS in Neuromuscular Disease inspector]() by `Hermien Kan`

### NMR Spectroscopy Course 

The course is given by ```James Keeler``` and includes 9 chapters and exercises.

- [Understanding NMR - Overview]()
- [NMR and Energy Levels]()
- [The Vector Model]()
- [FT and Data Processing]()
- [How the Spectrometer Works]()
- [Product Operators]()
- [2D NMR]()
- [Relaxation]()
- [Phase Cycling and Gradient Pulses]()
- [Exercises ]()



### Presentations 

- `Insensitive Nuclei Enhanced by Polarization TransferGareth (INEPT)` A. Morris and Ray Freeman JACS, 101, 1979, 760-762 [Link]()
- `Coupling constants` E. Kwan  [Link]()
- `Second Order Shimmingof High Field Magnets ` [Link]()


## Chapters and sub-chapters

There are two steps to cross-reference any heading:

1. Label the heading: `# Hello world {#nice-label}`. 
    - Leave the label off if you like the automated heading generated based on your heading title: for example, `# Hello world` = `# Hello world {#hello-world}`.
    - To label an un-numbered heading, use: `# Hello world {-#nice-label}` or `{# Hello world .unnumbered}`.

1. Next, reference the labeled heading anywhere in the text using `\@ref(nice-label)`; for example, please see Chapter \@ref(cross). 
    - If you prefer text as the link instead of a numbered reference use: [any text you want can go here](#cross).

## Captioned figures and tables

Figures and tables *with captions* can also be cross-referenced from elsewhere in your book using `\@ref(fig:chunk-label)` and `\@ref(tab:chunk-label)`, respectively.

See Figure \@ref(fig:nice-fig).

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center', fig.alt='Plot with connected points showing that vapor pressure of mercury increases exponentially as temperature increases.'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Don't miss Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(pressure, 10), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```
